### 2021-02-16 evaluation.tex
Extend a short table row
Reference the results table
Add a dummy row for function prec experiment
Add section Environment
Improve section Evaluation

To demonstrate the capacity of the precedence recommender described in \cref{sec:architecture},
a series of experiments was performed.
\todo{MS: vzdycky kdyz to jen trochu jde, snaz se pouzivat cinny rod (a pritomny cas): To demonstrate ..., we performed ... Ale taky tu trochu chybi, co nas ceka dal, ve stylu: In this section, we report ... }
In this section, we describe the design and configuration of the experiments,
and then compare the performance of the trained models to baseline heuristics.

@@

The empirical evaluation was performed using a modified version of the \gls{atp} Vampire 4.3.0.\cite{10.1007/978-3-642-39799-8_1}
The prover was used to generate the training data and to evaluate the trained precedence recommender.
To generate the training data,
Vampire was modified to output \gls{cnf} representations of the problems
and annotated problem signatures in a machine-readable format.
%in \gls{json} format and annotated problem signatures in \gls{csv} format.\todo{MS: Mentioning JSON or CSV seems to be too low level. ``programmer documatation'' material.}
For the evaluation of the precedences generated by the recommender,
Vampire was modified to allow the user to specify the predicate and function symbol precedences.
\todo[inline]{FB: Add a link to the modified Vampire.}

@@

\todo[inline,author=FB]{Describe the Vampire options.}
\todo{MS: Literal comparison mode is not a standard thing. Mentioning the option name is again too low level. Explaining the effect (point two) is appropriate, although a bit too vague. To kdyztak opravim ja. 
Popsat presne setup je dulezite, kvuli reprodukovatelnosti, ale ne nutne primo v clanku (budem nejspis stejne dodavat odkaz na nejake reproducibility repo).
Ted zminit AVATAR je nevhodne, pokud nevysvetlis, co to aspon ramcove je. A pokud to budes vysvetlovat, je otazka, proc tim ztracet misto, kdyz to neni bezprostredne relevantni pro dalsi vysvetlovani.}

@@

Since neither of the common \glspl{sot}, i.e., \gls{kbo} nor \gls{lpo}, ever compares a predicate symbol with a function symbol,
two separate precedences can be considered for each problem:
a predicate precedence and a function precedence.
A predicate precedence recommender is trained separately from a function precedence recommender
to simplify the training process and to isolate the effects of the predicate and function precedences.
This section describes how the training data for training a \emph{predicate} precedence recommender is generated.
Training data for training a function precedence recommender is generated analogously.

@@

The examples are generated by sampling the \gls{fol} part of the problem library \gls{tptp} v7.4.0.
A total of \num{17053} problems formulated in \gls{fof} and \gls{cnf} are sampled.
The problems formulated in \gls{fof} are converted to \gls{cnf} by Vampire.
% vampire --mode clausify
Let $\ProblemsTptp$ denote the set of all \num{17053} \gls{cnf} problems available for training and evaluation.

@@

The examples are generated by iterative sampling of $\ProblemsTptp$.
In each iteration, a problem $P \in \ProblemsTptp$ is chosen and Vampire is executed on $P$
with two predicate precedences chosen uniformly from the set of all predicate precedences on $P$.
A function precedence for $P$ is chosen uniformly and used for both executions.
\todo[author=FB]{Why do we sample function precedences randomly?}

The two executions are compared in terms of performance:
predicate precedence $\PrecBetter$ is recognized as better than precedence $\PrecWorse$,
denoted as $\Better{\PrecBetter}{\PrecWorse}$,
if the proof search finishes successfully with $\PrecBetter$ ($\SolverRun{P}{\Prec} = \top$)
and if the number of iterations of the saturation loop with $\PrecBetter$ is smaller than with $\PrecWorse$.
\todo{FB: Use notation for saturation loop iterations if the notation was established earlier. If failure is denoted by $\infty$, we can simply use $<$.}
If one of the two precedences is recognized as better,
the example $(P, \PrecBetter, \PrecWorse)$ is produced,
where $\PrecBetter$ is the better precedence,
and $\PrecWorse$ is the other precedence.

@@

@@

\begin{table*}
\caption{
Results of the evaluation of various predicate precedence heuristics on $\ProblemsVal$.
Means and standard deviations over 5 runs are reported.
}
\label{table:results}
\centering
\begin{tabular}{l|ll|ll}

@@

@@

\texttt{vampire -lcm standard} & ? & ? \\

\end{tabular}
\end{table*}
\todo{FB: Add links to Neptune runs?}
\todo{FB: Add results for function precedences.}
\todo{FB: Try to evaluate a recommender that uses both predicate and function models.}

>>>>

To demonstrate the capacity of the precedence recommender described in \cref{sec:architecture},
a series of experiments was performed.
%\todo{MS: vzdycky kdyz to jen trochu jde, snaz se pouzivat cinny rod (a pritomny cas): To demonstrate ..., we performed ... Ale taky tu trochu chybi, co nas ceka dal, ve stylu: In this section, we report ... }
In this section, we describe the design and configuration of the experiments,
and then compare the performance of the trained models to baseline heuristics.

@@

The empirical evaluation was performed using a modified version of the \gls{atp} Vampire 4.3.0 \cite{10.1007/978-3-642-39799-8_1}.
The prover was used to generate the training data and to evaluate the trained precedence recommender.
To generate the training data,
Vampire was modified to output \gls{cnf} representations of the problems
and annotated problem signatures in a machine-readable format.
%in \gls{json} format and annotated problem signatures in \gls{csv} format.\todo{MS: Mentioning JSON or CSV seems to be too low level. ``programmer documatation'' material.}
For the evaluation of the precedences generated by the recommender,
Vampire was modified to allow the user to specify the predicate and function symbol precedences
for the proof search.
\todo[inline]{FB: Add a link to the modified Vampire.}

@@

\todo[inline,author=FB]{Describe the Vampire options.}
\todo[inline,author=MS]{Literal comparison mode is not a standard thing. Mentioning the option name is again too low level. Explaining the effect (point two) is appropriate, although a bit too vague. To kdyztak opravim ja. 
Popsat presne setup je dulezite, kvuli reprodukovatelnosti, ale ne nutne primo v clanku (budem nejspis stejne dodavat odkaz na nejake reproducibility repo).
Ted zminit AVATAR je nevhodne, pokud nevysvetlis, co to aspon ramcove je. A pokud to budes vysvetlovat, je otazka, proc tim ztracet misto, kdyz to neni bezprostredne relevantni pro dalsi vysvetlovani.}

@@

Since neither of the common \glspl{sot}, i.e., \gls{kbo} nor \gls{lpo},
\todo{FB: Consider omitting LPO completely if we don't discuss it anywhere in the paper.}
ever compares a predicate symbol with a function symbol,
two separate precedences can be considered for each problem:
a predicate precedence and a function precedence.
A predicate precedence recommender is trained separately from a function precedence recommender
to simplify the training process and to isolate the effects of the predicate and function precedences.
\todo{FB: Weak, handwavy spot. Consider improving the argumentation.}
This section describes how the training data for training a \emph{predicate} precedence recommender is generated.
Training data for training a function precedence recommender is generated analogously.

@@

The examples are generated by sampling the \gls{fol} part of the problem library \gls{tptp} v7.4.0 \cite{10.1007/978-3-030-29436-6_29}.
A total of \num{17053} problems formulated in \gls{fof} and \gls{cnf} are sampled.
The problems formulated in \gls{fof} are converted to \gls{cnf} by Vampire.
% vampire --mode clausify
Let $\ProblemsTptp$ denote the set of all \num{17053} \gls{cnf} problems available for training and evaluation.

@@

The examples are generated by iterative sampling of $\ProblemsTptp$.
In each iteration, a problem $P \in \ProblemsTptp$ is chosen and Vampire is executed on $P$
with two predicate precedences chosen with uniform probability from the set of all predicate precedences on $P$.
One function precedence for $P$ is chosen with uniform probability, and it is used for both executions.
\todo[author=FB]{Why do we sample function precedences randomly?}

The two executions are compared in terms of performance:
predicate precedence $\PrecBetter$ is recognized as better than predicate precedence $\PrecWorse$,
denoted as $\Better{\PrecBetter}{\PrecWorse}$,
if the proof search finishes successfully with $\PrecBetter$ ($\SolverRun{P}{\Prec} = \top$)
and if the number of iterations of the saturation loop with $\PrecBetter$ is smaller than with $\PrecWorse$.
\todo{FB: Use notation for saturation loop iterations if the notation was established earlier. If failure is denoted by $\infty$, we can simply use $<$.}
If one of the two precedences is recognized as better,
the example $(P, \PrecBetter, \PrecWorse)$ is produced,
where $\PrecBetter$ is the better precedence,
and $\PrecWorse$ is the other precedence.

@@

\subsection{Environment}

All the experiments were run on a computer with the following specification:

\begin{itemize}
\item CPU: Intel Xeon Gold 6140 (72 cores @ \SI{2.30}{GHz})
\item RAM: \SI{383}{GiB}
\item OS: Ubuntu 20.04
\item Kernel: GNU/Linux 5.4.0-40-generic x86\_64
\end{itemize}

% From the paper Reliable benchmarking [BenchExec]:
% – CPU model and size of RAM,
% – specified resource limits,
% – name and version of OS,
% – version of important software packages, such as the kernel or runtime environments like the Java VM,
% – version and configuration of the benchmarked tool(s), and
% – version of the benchmark set (input files)

@@

\Cref{tab:results} shows the results.

\begin{table*}
\caption{
Results of the evaluation of various predicate precedence heuristics on $\ProblemsVal$.
Means and standard deviations over 5 runs are reported.
}
\centering
\begin{tabular}{l|ll|ll}

@@

\acrshort{gcn} (function) & ? & ? & \SI{51.2}{\percent} & ? \\
% TODO: This is a hot preview from VML-672. Replace with final results.

@@

\texttt{vampire -lcm standard} & ? & ? & ? & ? \\

\end{tabular}
\label{tab:results}
\end{table*}
\todo{FB: Add links to Neptune runs?}
\todo{FB: Finalize results for function precedences.}
\todo{FB: Try to evaluate a recommender that uses both predicate and function models.}
